Sex and Power: Sexual dimorphism in trait variability and its eco-evolutionary

### 2020-05-19 scripts/MouseSexDiffApril20_2020.Rmd
Updated colour scheme for mean-var

male <- ggplot(results, aes(x = lnMean_m, y = logSD_m)) +
    geom_point(color = "blue", size = 2) +
   geom_smooth(method = "lm", se = FALSE, color="black") + 
    labs(x = "log (Mean)",
         y = "log (SD)") + 
    theme_classic()

female <- ggplot(results, aes(x = lnMean_f, y = lnSD_f)) +
    geom_point(color = "pink", size = 2) +
  geom_smooth(method = "lm", se = FALSE, color="black")+
    labs(x = "log (Mean)",
         y = "log (SD)") + 
    theme_classic()

>>>>

male <- ggplot(results, aes(x = lnMean_m, y = logSD_m)) +
    geom_point(color = "#66C2A5", size = 2) +
   geom_smooth(method = "lm", se = FALSE, color="black") + 
    labs(x = "log (Mean)",
         y = "log (SD)") + 
    theme_classic()

female <- ggplot(results, aes(x = lnMean_f, y = lnSD_f)) +
    geom_point(color = "#FC8D62", size = 2) +
  geom_smooth(method = "lm", se = FALSE, color="black")+
    labs(x = "log (Mean)",
         y = "log (SD)") + 
    theme_classic()
